Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-14 manuscript/supplementaryRW.Rmd
update report PICUS

[4C
(v2.2)]([https://doi.org/10.5194/gmd-13-5311-2020)](https://doi.org/10.5194/gmd-13-5311-2020))
is usually not used for simulations of forest equillibrium dynamics,
potential natural vegetation assessment and long simulation periods but
rather shorter-term simulations (up to 100-150 years). In addition, only
five species out of the pool of eleven potentially relevant species here
are parameterized in 4C so that projections of the potential natural
vegetation done wih 4C need to be considered in the light of model
uncertainty.
For example, the spatial homogeneity in the model leads to
cyclic recruitment patterns (see Fig. 4). When the adult stands dies of,
young individuals are recruited into the larger diameter classes because
more light reaches lower canopy layer since larger (adult) trees do not
anymore prevent the light reaching lower canopy layers. This results in
increased growth of the regeneration layer during those times. In most
stands Fagus sylvatica dominates the stand after some time but
occasionally individuals of other species, like Picea abies or Quercus
spp. cross the recruitment diameter threshold.

@@

The most complete reference resource for the PICUS model and
regeneration module is:

@@

We used soil parameters as suggested by the protocol. Between given
class specific values linear interpolation was sued to find
between-class values. Soil Class N WHC pH 1 40 80 4.2 2 - - 4.2 3 - -
4.6 4 - - 5.6 5 100 250 5.6

@@

r.trees Counted the number of trees which were not present in the stand
from the previous time period (10 years before) and where above the dbh
threshold per species. For the oaks the value of the two species was
summed into one. The result was then divided by 1.44 to get a per ha
value of r.trees. r.ba Sum of the basal area (circle area calculated
with the dbh) of trees which were not present in the stand from the
previous time period (10 years before) and where above the dbh
threshold. This was then divided by 1.44 to get a per ha value. ba Sum
of the basal area (circle area calculated with the dbh) of all trees
above the dbh threshold. This was then divided by 1.44 to get a per ha
value.

>>>>

[4C
(v2.2)](%5Bhttps://doi.org/10.5194/gmd-13-5311-2020)](<https://doi.org/10.5194/gmd-13-5311-2020>))
is usually not used for simulations of forest equillibrium dynamics,
potential natural vegetation assessment and long simulation periods but
rather shorter-term simulations (up to 100-150 years). In addition, only
five species out of the pool of eleven potentially relevant species here
are parameterized in 4C so that projections of the potential natural
vegetation done wih 4C need to be considered in the light of model
uncertainty. For example, the spatial homogeneity in the model leads to
cyclic recruitment patterns (see Fig. 4). When the adult stands dies of,
young individuals are recruited into the larger diameter classes because
more light reaches lower canopy layer since larger (adult) trees do not
anymore prevent the light reaching lower canopy layers. This results in
increased growth of the regeneration layer during those times. In most
stands Fagus sylvatica dominates the stand after some time but
occasionally individuals of other species, like Picea abies or Quercus
spp. cross the recruitment diameter threshold.

@@

The core elements of PICUS are described in Lexer and Hönninger (2001)
and Seidl et al. (2005). Specific details regarding the regeneration
module can be found in Woltjer et al. (2008).

-   Lexer MJ, Hönninger K (2001) A modified 3D-patch model for spatially
    explicit simulation of vegetation composition in heterogeneous
    landscapes. For Ecol Manag 144:43--65.
    doi:10.1016/S0378-1127(00)00386-8

-   Seidl R, Lexer MJ, Jäger D, Hönninger K (2005) Evaluating the
    accuracy and generality of a hybrid patch model. Tree Physiol
    25:939--951. doi:10.1093/treephys/25.7.939

-   Woltjer M, Rammer W, Brauner M, Seidl R, Mohren GMJ, Lexer MJ (2008)
    Coupling a 3D patch model and a rockfall module to assess rockfall
    protection in mountain forests. J Environ Manag 87:373--388.
    doi:10.1016/j.jenvman.2007.01.031

@@

Based on the provided continuous value for soil quality between 1 and 5
minimum (soil quality = 1) and maximum (soil quality = 5) values for
soil water holding capacity (80mm, 200mm), plant available Nitrogen (40
kg ha^-1^ yr^-1^, 100 kg ha^-1^ yr^-1^) and soil pH (4.2, 5.6) were
defined. Linear interpolation was used to scale between the minimum and
maximum values.

@@

Output consisted of species-specific regeneration rates per decade and
per ha. Oak species were aggregated. A sample was taken for every 10
years for a total period of 2000 years once the model had reached
equilibrium (see 1.7.7.3). Ingrowth was determined by counting the trees
passing the 7cm and 10cm DBH thresholds every 10 years. Basal area of
the ingrowth was determined at the end of each decade.
